---
title: "Area-Days_v_Recharge"
author: "Alysa Yoder"
date: "1/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Get Inundation Vol. Data
```{r}
library(lubridate)
library(plotly)
library(here)
inundation_data <- read.csv(here::here("data", "Whipple_Hydrospatial_PostRestoration_wy2013-2017.csv"))
inundation_data$dt <- mdy(inundation_data$dt)
```

## Get Rech. Event Timeframes
```{r}

## Writing a df for all recharge event timeframes in 2013WY
event_pre13 <- data.frame(matrix(ncol = 4, nrow = 3))
cnames <- c("Event Number", "Start", "End", "Length")
colnames(event_pre13) <- cnames

#event_pre13$`Event Number` <- seq(1,3,1)
event_pre13$Start <- as.POSIXct(c("12/18/2012 22:00:00", "12/23/2012 02:45:00", "01/05/2013 21:45:00"), 
                                format = "%m/%d/%Y %H:%M")
event_pre13$End <- as.POSIXct(c("12/19/2012 20:00:00", "12/28/2012 14:00:00", "01/09/2013 02:00:00"), 
                                format = "%m/%d/%Y %H:%M")
#event_pre13$Length <- event_pre13$End - event_pre13$Start #leaving empty so they'll be consistent 
```

```{r pre removal dates}
## Writing a df for all recharge event timeframes in 2014WY
event_pre14 <- data.frame(matrix(ncol=4, nrow=4))
cnames <- c("Event Number", "Start", "End", "Length")
colnames(event_pre14) <- cnames
#event_pre14[ ,1] <- seq(1,4,1) #leaving blank, more efficient to do all at once after rbind
#these are start times of each event 
event_pre14[ ,2] <- as.POSIXct(c("02/09/2014 23:00:00", 
                                 "03/01/2014 02:00:00", 
                                 "03/02/2014 18:45:00", 
                                 "04/02/2014 15:45:00"),
                               format = "%m/%d/%Y %H:%M")
#these are end times of each event 
event_pre14[ ,3] <- as.POSIXct(c("02/12/2014 18:00:00", 
                                 "03/06/2014 15:30:00", 
                                 "03/08/2014 14:00:00", 
                                 "04/05/2014 16:00:00"),
                               format = "%m/%d/%Y %H:%M")
#event_pre14[ ,4] <- event_pre14[ ,3] - event_pre14[ ,2] #leaving these empty for now so units will be consistent
```

```{r}
## Writing a df of all pre-removal recharge event timeframes
event_pre <- rbind(event_pre13, event_pre14)
event_pre$`Event Number` <- seq(1,nrow(event_pre), 1)
event_pre$Length <- event_pre$End-event_pre$Start

```

```{r post removal}

event_post <- data.frame(matrix(ncol=4, nrow=19))
cnames <- c("Event Number", "Start", "End", "Length")
colnames(event_post) <- cnames
#event_post[ ,1] <- seq(1,4,1) #leaving blank, more efficient to do all at once after rbind
#these are start times of each event 
event_post[ ,2] <- as.POSIXct(c("12/12/2014 23:00:00", 
                                 "12/20/2014 14:45:00", 
                                 "02/08/2015 03:45:00", #last of 2015WY events
                                 "12/22/2015 23:15:00", 
                                "01/19/2016 00:15:00",
                                "01/23/2016 14:45:00",
                                "01/30/2016 12:00:00",
                                "02/19/2016 04:45:00",
                                "03/05/2016 13:45:00", #last of 2016WY events
                                "11/28/2016 19:45:00",
                                "12/11/2016 1:30:00",
                                "01/04/2017 19:00:00",
                                "01/18/2017 18:45:00",
                                "02/04/2017 07:15:00",
                                "02/20/2017 14:15:00",
                                "03/22/2017 15:00:00",
                                "04/07/2017 04:30:00",
                                "04/13/2017 19:00:00",
                                "04/18/2017 15:00:00"),
                               format = "%m/%d/%Y %H:%M")
#these are end times of each event 
event_post[ ,3] <- as.POSIXct(c("12/14/2014 16:45:00", 
                                 "12/22/2014 14:00:00", 
                                 "02/12/2015 15:45:00", #last of 2015WY events
                                 "12/23/2015 12:45:00",
                                "01/21/2016 02:30:00",
                                "01/25/2016 04:30:00",
                                "02/02/2016 12:00:00",
                                "02/19/2016 20:45:00",
                                "03/17/2016 13:00:00", #last of 2016WY events
                                "11/29/2016 03:00:00",
                                "12/21/2016 12:45:00",
                                "01/12/2017 14:00:00",
                                "01/24/2017 07:00:00",
                                "02/11/2017 09:00:00",
                                "02/22/2017 14:15:00",
                                "03/23/2017 16:15:00",
                                "04/09/2017 19:45:00", 
                                "04/15/2017 01:30:00",
                                "04/20/2017 03:45:00"), 
                               format = "%m/%d/%Y %H:%M")
#write df of all start and end dates w/proper headings
event_post$`Event Number` <- seq(1,nrow(event_post), 1)
event_post$Length <- event_post$End-event_post$Start
```

```{r combine pre and post event timestamps}
event <- rbind(event_pre, event_post)
#write.csv(event, file = "rch_evnts.csv")
```

### Calculate Aday values and send to a df
```{r}
source(here::here("inund_events2019", "Aday_fxn.R")) #calculates area*days using whipple km^2 data and event lengths
source(here::here("inund_events2019", "aday_evsub_fxn.R")) #creates Aday df with data from the specified time interval 

#add event ID column to DF for cleaner result communication
EventID <- seq(1,nrow(event),1)

Aday_dat <- data.frame(EventID) # event number in event_pre corresponds to the row numbers in Qdat. 

for (row in 1:nrow(event)) {
 Aday_dat[row, 2] <- Aday(ev_data = evsub(event[row,2], event[row,3]))
}
colnames(Aday_dat) <- c("Event #", "Area*Days")
Aday_dat
```

## Load recharge event data and add area*days to it for figure generation
```{r}
rechdat <- read.csv(here::here("data", "rech_ev_data.csv"))
rechdat$Aday_dat <- Aday_dat[,2]
rechdat$X <- NULL
```

## Make figure showing correlation of rech volume and area*days, grouped pre v post
```{r}
library(ggplot2)
ggplot(rechdat, aes(colour=factor(prevpost))) +
  geom_point(aes(x=rechdat$Aday_dat, y=rechdat$RechVol)) +
  scale_y_log10()+
  scale_x_log10()+
 # annotation_logticks(base=10, sides = 'bl', scaled =T, short=unit(0,1,'cm'))+
  geom_smooth(data=rechdat[1:7,], aes(x=rechdat$Aday_dat[1:7], y=rechdat$RechVol[1:7]),
method ="lm", se=T) +
  geom_smooth(data=rechdat[8:26,], aes(x=rechdat$Aday_dat[8:26], y=rechdat$RechVol[8:26]),
              method = "lm", se=T) +
  scale_colour_discrete(name = "Levee Removal Status", 
                        breaks=c(2,1),
                        labels=c("Pre-Removal", "Post-Removal")) +
  xlab(bquote('Area*Days'))+
  ylab(bquote('Recharge Volume ('~m^3~') (log)'))+
  theme_set(theme_bw(base_size=20))+
  theme(legend.position = "top")

```

## Correlation of area*days with recharge volume of each event, not grouped
```{r}
library(ggplot2)
ggplot(rechdat) +
  geom_point(aes(x=rechdat$Aday_dat, y=rechdat$RechVol)) +
 #scale_y_log10()+
#scale_x_log10()+
 # annotation_logticks(base=10, sides = 'bl', scaled =T, short=unit(0,1,'cm'))+
  geom_smooth(data=rechdat, aes(x=rechdat$Aday_dat, y=rechdat$RechVol),
method ="lm", se=T) +
  xlab(bquote('Area*Days ('~km^2~'*day) (log)'))+
  ylab(bquote('Recharge Volume ('~m^3~') (log)'))+
  theme_set(theme_bw(base_size=20))+
  theme(legend.position = "top")
```

## Code from previous cumulative discharge v. recharge figure 
```{r{}}
library(ggplot2)
#devtools::source_gist("524eade46135f6348140", filename = "ggplot_smooth_func.R")
ggplot(agree,aes(colour=factor(prevpost))) + 
  
  geom_point(aes(x=agree$Cumul.Dis, y=agree$RechVol)) +
 scale_y_log10()+
  scale_x_log10()+
  annotation_logticks(base=10, sides = 'bl', scaled = TRUE, short=unit(0.1, "cm"))+
  geom_smooth(data=agree[1:7,], aes(x=agree$Cumul.Dis[1:7], y=agree$RechVol[1:7]), 
              method="lm", se=T) +
  geom_smooth(data=agree[8:26,], aes(x=agree$Cumul.Dis[8:26], y=agree$RechVol[8:26]), 
              method="lm", se=T) +
  scale_colour_discrete(name="Levee Removal Status", 
                        breaks=c(2,1),
                        labels=c("Pre-Removal", "Post-Removal")) +
  #labs(title = "Recharge Volume vs. Cumulative Discharge",
 # subtitle="Throughout Each Recharge Event, 2013-2017") +
       xlab(bquote('Cumulative Discharge ('~m^3~') (log)')) +
       ylab(bquote('Recharge Volume ('~m^3~') (log)')) +
    theme_set(theme_bw(base_size = 20))+
theme(legend.position = "top") 
```