---
title: "Recharge Function Applications"
author: "Alysa M. Yoder"
date: "June 25, 2018"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
    theme: flatly
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(warning = FALSE, 
                      message = FALSE,
                      error = FALSE, 
                      cache = TRUE, 
                      eval = TRUE)
library(here)
```

## Notes
Supplementary material to the recharge volume calculator function.
Actual function is in rech_fxn.R, this 'rech_fxn.Rmd' has the formatting and its where I'll actually do the calculations of recharge. 

> Rules

* import water levels at the beginning and end of the event
* input files' columns must be in this order: lat, long, level
* the 'level' column must be in meters of groundwater elevation relative to mean sea level

***

# Get Groundwater Level Data
```{r}
adata <- read.csv(here::here('data', 'allsets.csv'))
adata <- adata[-c(1,3,15,17:31)] #removing index numbers, MW-13, Oneto-Ag (confined), and Nathan's text 
```

# Call Functions
```{r}
source('rech_fxn.R')
source('rechcalc_gwl_format.R')
```

# Comparison of Similar Event Pre&Post Levee Removal
Why is it returning larger than actual changes in water level at MW23 and MW 17? 

* Subset was converting numeric water levels to factor, this is now fixed in the formatting function by converting this column back to numeric. 
```{r}
#recharge event max and min GWLs pre-removal, during the 2014 WY
evlo14 <- as.data.frame(t(subset(adata, Date == "2014-02-10 02:15:00")))
evhi14 <- as.data.frame(t(subset(adata, Date == "2014-02-12 05:30:00")))
#clean up data to get just water levels
#low
evlo14 <- rechcalc_gwl_format(evlo14)
#high
evhi14 <- rechcalc_gwl_format(evhi14)
#use function for 2014 event 
rechvol(begin = evlo14, end = evhi14, plot_title = "2014WY Event")

#repeat all for 2015 WY
evlo15 <- as.data.frame(t(subset(adata, Date == "2014-12-12 21:15:00")))
evhi15 <- as.data.frame(t(subset(adata, Date == "2014-12-14 09:30:00")))
#clean up data to get just water levels
#low
evlo15 <- rechcalc_gwl_format(evlo15)
#high
evhi15 <- rechcalc_gwl_format(evhi15)
#use function for 2014 event 
rechvol(begin = evlo15, end = evhi15, plot_title = "2015WY Event")

```

# Look at flood vols on a day during each event
```{r}
library(raster)
library(rgdal)
library(dplyr)
fld14 <- raster(here::here("rasters", "predicted_post_Depth_2014.02.11_3m.grd"), package = "raster")
p1 <- spplot(fld14, col.regions = rev(get_col_regions()), main = "2014 Event Flooding", at = seq(0,1.5, by = 0.1))

fld15 <- raster(here::here("rasters", "predicted_post_Depth_2014.12.13_3m.grd"), package = "raster")
p2 <- spplot(fld15, col.regions = rev(get_col_regions()), main = "2015 Event Flooding", at = seq(0,1.5, by = 0.1))
#plot both days of flooding side by side for comparison
print(p1, position = c(0, 0, .5, 1), more = TRUE)
print(p2, position = c(.5, 0, 1, 1))
```

# Determine volume of flooding on a day during each event
```{r}
#each cell is 3x3
c_a <- 9
# m3 per cell
totm3_14 <- cellStats((c_a * fld14), "sum")
totm3_15 <- cellStats((c_a * fld15), "sum")
#show results in table
t <- matrix(c(totm3_14, totm3_15), ncol=1)
colnames(t) <- "Floodwater Volume m^3"
rownames(t) <- c("2014WY", "2015WY")
t <- as.table(t)
kable(t)
```

# Determine avg flood volume throughout event w/weighted avg
```{r}
fl1_14 <- raster(here::here("rasters", "predicted_post_Depth_2014.02.10_3m.grd"), package = "raster")
pr1_14 <- (24-2.25)/24 #proportion of this day covering the event
fl2_14 <- raster(here::here("rasters", "predicted_post_Depth_2014.02.11_3m.grd"), package = "raster")
pr2_14 <- 1
fl3_14 <- raster(here::here("rasters", "predicted_post_Depth_2014.02.12_3m.grd"), package = "raster")
pr3_14 <- 5.5/24

fl1_15 <- raster(here::here("rasters", "predicted_post_Depth_2014.12.12_3m.grd"), package = "raster")
pr1_15 <- (24-21.25)/24
fl2_15 <- raster(here::here("rasters", "predicted_post_Depth_2014.12.13_3m.grd"), package = "raster")
pr2_15 <- 1
fl3_15 <- raster(here::here("rasters", "predicted_post_Depth_2014.12.14_3m.grd"), package = "raster")
pr3_15 <- 9.5/24
#2014 flood vol each day 
v1_14 <- cellStats((9 * fl1_14), "sum") #sum of the day's floodwater volume 
v2_14 <- cellStats((9 * fl2_14), "sum")
v3_14 <- cellStats((9 * fl3_14), "sum")
#2015 flood vol each day
v1_15 <- cellStats((9 * fl1_15), "sum") 
v2_15 <- cellStats((9 * fl2_15), "sum")
v3_15 <- cellStats((9 * fl3_15), "sum")

#weighted avg for 2014 event
wtdvol14 <- (v1_14*pr1_14) + (v2_14*pr2_14) + (v3_14*pr3_14)
#weighted avg for 2015 event
wtdvol15 <- (v1_15*pr1_15) + (v2_15*pr2_15) + (v3_15*pr3_15)
#put results in table
wt <- matrix(c(wtdvol14, wtdvol15), ncol=1)
colnames(wt) <- "Avg Floodwater Vol During Event (m^3)"
rownames(wt) <- c("2014WY", "2015WY")
wt <- as.table(wt)
kable(wt)
```

# Determine Integrated Discharge (Mich Bar) Throughout Flood Event
```{r}
library(here)
library(dplyr)
library(kableExtra)
mb <- read.csv(here::here("data", "mich_bar_cms_all.csv"), stringsAsFactors = FALSE)
mb$Date <- as.POSIXct(mb$Date, format = "%m/%d/%Y %H:%M")
#subset discharge data to the length of each flooding event, creating data frames mb14 and mb15
mb14 <- mb %>% 
  select(Date, MiBarCMS) %>%
  filter(Date >= as.POSIXct("2014-02-10 02:15:00") & Date <= as.POSIXct("2014-02-12 05:30:00"))
mb15 <- mb %>% 
  select(Date, MiBarCMS) %>%
  filter(Date >= as.POSIXct("2014-12-12 21:15:00") & Date <= as.POSIXct("2014-12-14 09:30:00"))
#calculate integrated volume of discharge throughout the event 
qvol14 <- sum(mb14$MiBarCMS)*((15*60)*nrow(mb14)) #multiply the total number of seconds by the sum of m^3/s 
qvol15 <- sum(mb15$MiBarCMS)*((15*60)*nrow(mb15))
vols <- matrix(c(qvol14,qvol15), ncol=1)
colnames(vols) <- "Integrated Discharge Vol at Mich Bar (m^3)"
rownames(vols) <- c("2014 Event", "2015 Event")
vols <- as.table(vols)
kable(vols) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = F, position = "left")
```

# Get Lat Long Coordinates for Each Well, this also happens inside 'rechcalc_gwl_format.R' function
```{r, include= FALSE}
# format dataframes w/lat long 
label <- read.csv(here('data', "MW_label_allsets.csv"), header = F) #get lat long data, already in order of allsets.csv wells
label[3] <- NULL #removes well ID text column, leaving only lat long coords
```

# Get Data from Desired Dates
```{r, include=FALSE}
# grab max and mins from each water year. 
max2014 <- as.data.frame(t(subset(adata, Date == "2014-05-10 12:00:00")))
min2014 <- as.data.frame(t(subset(adata, Date == "2014-02-09 12:00:00")))

max2015 <- as.data.frame(t(subset(adata,Date =="2015-04-12 12:00:00")))
min2015 <- as.data.frame(t(subset(adata,Date =="2014-12-04 12:00:00")))

max2016 <- as.data.frame(t(subset(adata,Date =="2016-03-18 12:00:00")))
min2016 <- as.data.frame(t(subset(adata,Date=="2015-12-10 12:00:00")))

min2017 <- as.data.frame(t(subset(adata,Date=="2016-10-19 12:00:00")))
max2017 <- as.data.frame(t(subset(adata,Date=="2017-02-11 12:00:00")))

```